Supplement 2

### 2020-09-08 paper/supplement-2.Rmd
update data extraction table. update search results and conclusion.

Articles were surveyed to determine: (a) whether a missing data
statement was included, or if missing data were acknowledged in a
figure/table; (b) where data were missing, whether data were considered
MCAR, MAR or MNAR; (c) whether imputation was used, and the imputation
method; and (d) whether articles that did not include a missing data
statement shared their data. Two authors independently extracted the
data. Agreement was X%; discrepancies were resolved by NJT. Findings are
reported as the proportion and 95% confidence interval (CI). Confidence
intervals were calculated using the Clopper-Pearson method for the
binomial distribution [@Clopper1934],via the 'binom' package [@binom] in R (version 4.0.2) [@rcore].

@@

The search returned a total of 3,863 articles (Figure 1). Of the 199
articles screened, 136 were deemed eligible, representing \~10% of total
articles published on football related studies in 2019 (Figure X). The
proportion of articles that included a missing data statement (or
acknowledged missing data in a table/figure) was 5.9% \[95% confidence
interval; X% to X%\] or 8/136. A breakdown of the extracted information
is provided in Table XX.

@@

extractions <- tibble(
  Imported = 3863,
  `After duplicates removed` = 1954,
  `After title and abstract screen` = 1373,
  `Random sample full-text` = "199 for 10% sample",
  `Full-text included` = 137,
  `Full-text excluded` = 62
)

@@

A survey of 136 articles published in 2019, on football related topics
showed that only one in 20 reported missing data. This result suggests
that missing data are rarely considered by sport science researchers.

>>>>

Articles were surveyed to determine: (a) whether a missing data
statement was included, or if missing data were acknowledged in a
figure/table; where data were missing, whether (b) data were considered
MCAR, MAR or MNAR; (c) imputation was used; (d) the method used for imputation; 
and (e) whether articles that did not include a missing data
statement shared their data. Two authors independently extracted the
data. Agreement was X%; discrepancies were resolved by NJT. Findings are
reported as the proportion and 95% confidence interval (CI). Confidence
intervals were calculated using the Clopper-Pearson method for the
binomial distribution [@Clopper1934],via the 'binom' package [@binom] in R (version 4.0.2) [@rcore].

@@

The search returned a total of 3,863 articles (Figure 1). Of the 199
articles screened, 137 were deemed eligible, representing \~10% of total
articles published on football related studies in 2019 (Figure 1). The
proportion of articles that reported missing data was 5.9% \[95% confidence
interval; X% to X%\] or 8/136. A breakdown of the extracted information
is provided in Table 2.

@@

extractions <- tibble( # This is Table 2
  `Missing data reported` = "XX",
  `Type of missingness reported (i.e., MCAR, MAR or MNAR)` = "XX",
  `Missing data explored` = "XX",
  `Missing observations imputed` = "XX",
  `Imputation method` = "XX",
  `Data shared` = "XX"
)

@@

A survey of 137 articles published in 2019 on football related topics
showed that only one in 20 reported missing data, suggesting
that missing data are rarely considered by sport science researchers.
